A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-14 main.tex
before \textit{P} value

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis. There is some optimization software for cutoff determination. However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses. There are few clinicopathological features available on their pre-processed data sets.
We developed a comprehensive workflow that includes data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes. After adjustment with confounders and Bonferroni adjusted P-value, ten candidate biomarkers, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival. At the same time, the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
We suggest this workflow could help for biomarker discovery.
}

@@

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression. There is some optimization software for cutoff determination. However, that software's predetermined cutoffs have been set at the median or quantiles of RNA sequencing value to perform the survival analysis. 
%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
We developed a comprehensive workflow to perform biomarker discovery. It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected P-value.
The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
are significantly associated with a poor prognosis of overall survival. 
Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
We suggest this workflow could help for biomarker discovery.
}

@@

\subsection{holistic}
TCGA 都是手術後？TNM available yes
discussion: limitation
the TCGA has not collected holistic features
癌症與身心靈的重要關係：中醫、citation?
repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
自他不二
心存正念
1.衷心懺悔
2.真心感謝
3.誠意祝福
4.永存善念
5.心無恐懼: 情志養生

祝福全世界
